Stability and accuracy of free surface time integration in viscous flows

### 2016-09-04 free-surface-paper.tex
Remove comment.

We also investigate the advantages of combining adaptive mesh refinement with free surface computations.
\citet{crameri2012comparison} performed a community benchmark of a setup for which there is no analytic
solution. In this benchmark, a buoyant blob rises beneath a viscous lid with a free surface, deflecting the
boundary upwards, reminiscent of the dynamic topography due to a rising plume (for the full setup, see \citet{crameri2012comparison}). 
Figure~\ref{fig:amr} shows the convergence of the maximum topography at 3 Myr to its value in a high resolution simulation,
both with and without adaptive mesh refinement.

>>>>

We also investigate the advantages of combining adaptive mesh refinement with free surface computations.
\citet{crameri2012comparison} performed a community benchmark of a setup for which there is no analytic
solution. In this benchmark, a buoyant blob rises beneath a viscous lid with a free surface, deflecting the boundary upwards.
Figure~\ref{fig:amr} shows the convergence of the maximum topography at 3 Myr to its value in a high resolution simulation,
both with and without adaptive mesh refinement.
